---
title: "Chapters 9: Types of Data Science Questions and 10. How to Learn"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyr)
library(dplyr)
knitr::opts_chunk$set(echo = TRUE)
tutorial_options(exercise.checker = NULL)
```


## Chapter 9: Types of Data Science Questions

### 9.0.0 Introduction

```{r quiz0, echo=FALSE}
quiz(
  question("Which type of data science question aims to find unknown relationships between different variables?",
    answer("Descriptive"),
    answer("Exploratory", correct = TRUE),
    answer("Inferential"),
    answer("Predictive"),
    allow_retry = TRUE
  ),
    question("What is the term for a seemingly related relationship between two variables that are not actually causally related?",
    answer("Casual correlation"),
    answer("Strong correlation"),
    answer("Spurious correlation", correct = TRUE),
    answer("Direct correlation")
  ),
  question("What is the term for a seemingly related relationship between two variables that are not actually causally related?",
    answer("Casual correlation"),
    answer("Strong correlation"),
    answer("Spurious correlation", correct = TRUE),
    answer("Direct correlation")
  )
)
```


### 9.0.1 Examples of data science questions

```{r quiz3, echo=FALSE}
quiz(
  question("What type of analysis is used for credit card fraud detection?",
    answer("Descriptive analysis"),
    answer("Exploratory analysis"),
    answer("Inferential analysis"),
    answer("Predictive analysis", correct = TRUE),
    allow_retry = TRUE
  )
)
```


```{r quiz4, echo=FALSE}
quiz(
  question("What type of analysis is used for analyzing YouTube comments?",
    answer("Descriptive analysis", correct = TRUE),
    answer("Exploratory analysis"),
    answer("Inferential analysis"),
    answer("Predictive analysis")
  )
)
```


```{r quiz5, echo=FALSE}
quiz(
  question("What type of analysis is used for analyzing the relationship between watching Sesame Street and children's test scores?",
    answer("Descriptive analysis"),
    answer("Exploratory analysis"),
    answer("Inferential analysis", correct = TRUE),
    answer("Predictive analysis")
  )
)
```

## Chapters 10: How to Learn

In this tutorial, we will discuss the importance of learning how to learn, embracing failure, having the right mindset, and asking for help.

### 10.0.1 Learning How To Learn

The best way to learn data science is by doing it. Throughout these lessons, practice the code you see and try it out on your own. If you get an error, that's okay! Google that error and try to learn from it!

### 10.0.1.1 The Mindset

Your mindset is very important to learning how to learn. Your goal should be to answer an interesting question. Your objective is not to memorize a bunch of functions but to use those functions to do something interesting. The path to accomplishing that goal may be circuitous, and you may experience setbacks before moving forward. That's okay!


### 10.0.1.2 The Path

When carrying out data science projects, there is always more than one way to solve a problem. Your path may be different from someone else's path. There is more than one way to approach and answer a question! Your approaches may not be identical, and that is more than okay!


### 10.0.1.3 Asking For Help

Data science is best done as a part of a community! Asking questions and brainstorming with others is ideally how data science projects are completed. No one knows everything, and that is okay and expected. When you're stuck, reach out for help, post your question online, or ask someone directly.


```{r quiz6, echo=FALSE}
quiz(
  question("What is an important aspect of learning how to learn?",
    answer("Memorizing functions", correct = FALSE),
    answer("Embracing failure and having the right mindset", correct = TRUE),
    answer("Never asking for help", correct = FALSE)
  ),
  question("Which statement is true?",
    answer("There is only one correct way to solve a data science problem", correct = FALSE),
    answer("There can be multiple ways to solve a data science problem", correct = TRUE)
  ),
  question("When should you ask for help?",
    answer("Immediately without trying to solve the problem yourself", correct = FALSE),
    answer("After spending some time trying to solve the problem and searching online for a solution", correct = TRUE),
    answer("Never", correct = FALSE)
  )
)
```

In this tutorial, we discussed the importance of learning how to learn, embracing failure, having the right mindset, and asking for help. Remember that the best way to learn data science is by doing it, and don't be afraid to ask questions or seek help when you need it. Keep practicing and learning from your failures, and you'll improve your data science skills over time. Good luck!


## Congratulations!

Congratulations! You have completed the tutorial on understanding the data science process and are ready to start formulating more specific data science questions.
