---
title: "Chapters 7 - 12"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
tutorial_options(exercise.checker = NULL)
```


## 7. Forming Questions

### Learning Objectives

Through the completion of this section our goal is that you will be able to:

1. Recognize the general steps involved in a data science project
2. Practice forming data science questions
3. Understand the general categories for types of data science questions
4. Look at data and ask questions based on its contents

## 8 The Data Science Process

### 8.0.1 The Parts of a Data Science Project

```{r ex1, echo=FALSE}
```


### 8.0.2 A Data Science Project Example

```{r ex2, echo=FALSE}

```


#### 8.0.2.3 Data Analysis

```{r ex3, echo=FALSE}

```


#### 8.0.2.6 Get stats

```{r ex4, echo=FALSE}

```


#### 8.0.2.7 Interpret and communicate results

```{r ex5, echo=FALSE}

```


### 8.0.3 What you can build using R

#### 8.0.3.1 Prediction Risk of Opioid Overdoses in Providence, RI

```{r ex6, echo=FALSE}

```


### 8.0.4 Other Cool Data Science Projects

#### 8.0.4.1 Predicting movie ratings with IMDb data and R, by Dimiter Toshkov

```{r ex7, echo=FALSE}


```



## Chapter 9: Types of Data Science Questions

### 9.0.0 Introduction

```{r ex8, echo=FALSE}

```


### 9.0.1 Examples of data science questions

```{r ex9, echo=FALSE}
```


```{r ex10, echo=FALSE}
```


```{r ex11, echo=FALSE}

```

## Chapters 10: How to Learn

In this tutorial, we will discuss the importance of learning how to learn, embracing failure, having the right mindset, and asking for help.

### 10.0.1 Learning How To Learn

The best way to learn data science is by doing it. Throughout these lessons, practice the code you see and try it out on your own. If you get an error, that's okay! Google that error and try to learn from it!

### 10.0.1.1 The Mindset

Your mindset is very important to learning how to learn. Your goal should be to answer an interesting question. Your objective is not to memorize a bunch of functions but to use those functions to do something interesting. The path to accomplishing that goal may be circuitous, and you may experience setbacks before moving forward. That's okay!


### 10.0.1.2 The Path

When carrying out data science projects, there is always more than one way to solve a problem. Your path may be different from someone else's path. There is more than one way to approach and answer a question! Your approaches may not be identical, and that is more than okay!


### 10.0.1.3 Asking For Help

Data science is best done as a part of a community! Asking questions and brainstorming with others is ideally how data science projects are completed. No one knows everything, and that is okay and expected. When you're stuck, reach out for help, post your question online, or ask someone directly.


```{r ex12, echo=FALSE}

```

## Chapter 11 RStudio and Projects

In this interactive tutorial, we will go through Chapter 11 of the course, focusing on RStudio and Projects.

### Logging in to RStudio Cloud

```{r ex13, echo=FALSE}

```


### Logging in to RStudio Cloud

```{r ex14, echo=FALSE}

```


### Making a new folder

```{r ex15, echo=FALSE}

```


### Files/Help/Plots/Packages/Viewer

```{r ex16, echo=FALSE}

```


### Swirl


```{r ex17, echo=FALSE}

```

## Chapter 12: Your First Data Science Project

```{r ex18, echo=FALSE}

```


