---
title: "Chapters 76 - 82"
output:
  learnr::tutorial:
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)



knitr::opts_chunk$set(echo = TRUE)

gradethis::gradethis_setup()
```


## Chapter 76: Projecting from a Chromebook

As a data scientist, presenting your analysis is a common task. This tutorial will guide you on how to connect your Chromebook to a projector.

### Finding the right adapter

Connecting your Chromebook to a projector requires an adapter, commonly known as a "dongle". You need to identify the type of projector input (typically VGA or HDMI) and the available port on your Chromebook. To discover your Chromebook's port, visit https://www.google.com/chromebook, click "Find Yours", locate your model, and click on the BestBuy link for detailed information.

The recommended setup is to have two dongles: one with a VGA connection and the other with an HDMI connection. This will prepare you for most projector types.

### Projecting from your Chromebook

With the right dongle, you're set to project from your Chromebook. Connect the dongle to the projector cord, then to your Chromebook's port. A window titled "Extending screen to" will appear; click it to open the display settings.

You can set up the projector as an "Extended Display" or "Mirrored Display".

* "Extended Display": The projected screen acts as a second Desktop.
* "Mirrored Display": The projector mirrors your Desktop exactly.

For presentations, "Mirrored Display" is typically preferred.


## Chapter 77: Data Science Presentation for General Audiences

#### The Audience

When presenting to a general audience, such as individuals focused on day-to-day operations or high school students getting their first introduction to data science, it's crucial to consider their knowledge level. These individuals might not have a deep understanding of data science or quantitative analysis.

#### The Goal

The aim of your presentation should be to provide a high-level overview of your work. While it's still crucial to inspire, educate, and entertain, the nitty-gritty details of your analysis may not be as important to a general audience.

### The Presentation

The way you present your information is critical. In this section, we'll discuss what to emphasize and de-emphasize in your presentation.

#### Emphasize

When presenting to a general audience, your presentation should tell a story. Spend more time on the background and introduction, explaining:

* Why you conducted the analysis.
* Why your audience should care.
* The specific question you set out to answer.

#### De-emphasize

In a presentation for a general audience, avoid diving too deep into:

* The details of your approach.
* The problems you encountered during your analysis.

```{r ex2, echo=FALSE}
quiz(
  question("What is the primary goal of presenting to a general audience?", 
            answer("To explain the minute details of your analysis."),
            answer("To show off your coding skills."),
            answer("To provide a high-level overview of your work.", correct = TRUE),
            answer("To demonstrate all the problems you encountered during your analysis.")
  ),
  question("What should you emphasize in your presentation?",
            answer("The problems encountered during your analysis."),
            answer("The specific question you set out to answer.", correct = TRUE),
            answer("Your coding skills."),
            answer("Every single detail of your analysis.")
  )
)
```

#### Conclusion

Remember, presenting to a general audience is about conveying the core of your work without getting lost in the details. Keep it high-level, focused, and engaging!


## Chapter 78: How to present to a Technical Audience

#### Understanding the Audience

Technical presentations are typically delivered to an audience familiar with your work, such as team members or conference attendees in your specific field of expertise. Thus, you can often limit the amount of introductory material in this type of presentation and focus on the details of your analysis.

#### The Goal of the Presentation
The goal of a technical presentation is to explain the details of what you did. The emphasis should be on the details and caveats of your approach.

#### Structure of the Presentation
Like any good presentation, a technical presentation should have a clear beginning, middle, and end. The middle part, where you explain the details of your analysis, is where you should focus most of your attention.

#### Main Components of the Presentation
In a technical presentation, you need to provide your audience with:

1. A detailed summary of the data (descriptive + exploratory analysis)
2. What you did (with concrete details)
3. What you found (with multiple figures discussing results)
4. Discussion of the analysis
5. Conclusion

#### Emphasis and De-emphasis

In a technical talk, it's okay to de-emphasize certain background information that is common knowledge to everyone in the room. Instead, the bulk of your time and focus should be spent discussing the details of the analysis and its results.

```{r ex3, echo=FALSE}
quiz(
  question("What is the primary focus of a technical presentation?",
  answer("The presenter's credentials"),
  answer("Detailed summary of the data, the approach, the findings, analysis discussion, and conclusion", correct = TRUE),
  answer("Background information"),
  answer("The presenter's future plans")
),
  question("What information can be de-emphasized in a technical presentation?",
  answer("The presenter's credentials"),
  answer("Background information that is common knowledge", correct = TRUE),
  answer("The findings"),
  answer("The approach used in the analysis")
)
)
```

## Chapter 79: How to write a Blog Post

### What is a Blog Post?

A blog post is a piece of writing that is shared on the internet. It does not have to be as formal or as polished as a published article or academic paper. It can vary in length and depth, ranging from a short, simple example to a longer, more in-depth, and polished piece.

```{r ex4, echo=FALSE}
quiz(
  question("What is a blog post?",
    answer("A formal academic paper"),
    answer("A piece of writing shared on the internet", correct = TRUE),
    answer("A published article"),
    answer("An email")
  )
)

```

### General Outline of a Blog Post
A good blog post should tell a story. It should start with an introduction, followed by the main body broken down into sections, and end with a conclusion. The introduction should explain the topic and its importance. The body should logically present your points, and the conclusion should provide the key takeaways.

### Types of Blog Posts

There are many types of blog posts. Here, we will discuss four main types that are common in data science:

1. Announcement: These posts provide information about a new tool, dataset, or resource that might be useful to the community.
2. How-To: These are tutorial posts that teach how to do something, often including all necessary information and code.
3. Analysis: These posts present an interesting analysis that the author has conducted, often sharing code and results.
4. Workflow: These posts describe the author's workflow, offering insight into how they work on their computers and analyze data.

```{r ex5, echo=FALSE}
quiz(
  question("Which of these is NOT a common type of data science blog post?",
    answer("Announcement"),
    answer("How-To"),
    answer("Analysis"),
    answer("Recipe", correct = TRUE)
  )
)
```

### Why Write a Blog Post?
Writing a blog post can help you clarify and organize your thoughts, and it can also be a learning tool for others. Additionally, with the reach of the internet, your blog post can potentially be read by a huge audience.

#### Blog Etiquette
When writing a blog post or commenting on others' work, always be respectful and kind. Criticism should be limited to the work itself, and personal attacks should be avoided.

### Summary

In this tutorial, we've introduced the concept of a blog post, discussed the general outline of a blog post, explored different types of blog posts, and talked about the benefits of writing a blog post as well as the etiquette to maintain.

Remember, when writing a blog post:

* Have an informative title
* Include hyperlinks and references to others' work
* Separate sections with headers
* Include good figures
* Use clear, concise language


## Chapter 80: Participating in Meetings

#### Meeting Etiquette
In any meeting, there are general guidelines to follow:

1. Punctuality: Ensure to arrive, start, and end the meeting on time.
2. Conciseness: Keep your contributions precise and to the point.
3. Respectfulness: Avoid interrupting others and talking over them.
4. Positivity: Disagree constructively and appreciate others' work.
5. Problem-solving: If you identify a problem, offer a potential solution.


#### Hosting a Meeting

When hosting a meeting, careful planning is required. Key steps include:

1. Deciding if a meeting is necessary.
2. Drafting and distributing an agenda.
3. Deciding the meeting's date, time, and venue.
4. Identifying and inviting the necessary participants.
5. Keeping the meeting on track and ending it on time.

#### Participating in a Meeting

As a participant, your responsibilities include:

1. Paying attention and taking notes.
2. Participating actively and respectfully.
3. If presenting, be mindful of time, be prepared, and guide the discussion effectively.

```{r ex6, echo=FALSE}
quiz(
question("What are the key steps to consider when hosting a meeting?",
  answer("Deciding if a meeting is necessary"),
  answer("Drafting and distributing an agenda"),
  answer("Deciding the meeting's date, time, and venue"),
  answer("Identifying and inviting the necessary participants"),
  answer("All of the above", correct = TRUE)
),
question("What are the responsibilities of a participant in a meeting?",
  answer("Paying attention and taking notes"),
  answer("Participating actively and respectfully"),
  answer("If presenting, being mindful of time, prepared, and guiding the discussion effectively"),
  answer("All of the above", correct = TRUE)
)
)
```

## Chaper 81: How to Have a One-on-One Meeting

#### Consulting

One-on-one meetings, often referred to as consulting, involve discussions between two individuals: one seeking assistance and the other with data science expertise. These meetings aim to address specific questions and provide solutions using data analysis skills.

Consulting meetings typically last from 10 to 60 minutes, depending on the complexity of the question. Before the meeting, you can request relevant information or access to the dataset to prepare adequately. However, initial meetings might involve introductory discussions without requiring extensive preparation.

#### Navigating the Meeting

During the meeting, it's crucial to maintain professional etiquette and respect. Remember to be punctual, attentive, and considerate, just as in any other meeting. Recognize that both you and the person seeking your help have different knowledge backgrounds, and approach the discussion with openness and respect for each other's expertise.

#### The Investigation

The initial stage of the meeting is like an investigation. Your role is to:

1. Identify the specific question they want to ask.
2. Determine their prior knowledge and understanding of the question.
3. Assess the data they have available.
4. Understand their expectations for future data.
5. Evaluate whether the question can be answered with the available data.
6. Consider any constraints or limitations of the data.

#### Crafting the Question

People often approach you with vague questions. Your responsibility is to help formulate a specific data science question using the principles learned in data analysis courses. Through discussion, explain the importance of specificity to ensure a focused and answerable question.

#### Understanding Prior Knowledge
Take time to understand what the person seeking help already knows about the topic. Listen actively and learn from their experiences and work. This learning process helps establish a solid foundation for the project.


#### Assessing the Data
In many cases, individuals seek assistance after collecting the data. During the meeting, determine the data they currently possess and discuss how to tidy and format it for analysis. Additionally, explore any plans for future data collection and discuss the best data format for analysis.

#### Planning the Analysis
Based on the available data and the question of interest, decide on the most suitable analysis approach. Consider variables, missing data, outliers, and potential confounders. During this stage, your role is to teach and explain concepts clearly to ensure mutual understanding.

#### Acknowledging Limitations
Always consider the limitations of the analysis. Compare the actual data with the ideal dataset necessary to answer the question. By acknowledging and discussing these limitations upfront, you can avoid over-interpreting the findings later on.

Checklist for the Meeting
To ensure a productive meeting, use this checklist as a guide:

* Determine a specific question.
* Discuss the required information to answer the question.
* Decide on the variables for analysis.
* Assess the currently available data.
* Determine if the data is in a tidy format.
* Discuss future data availability.
* Address limitations of the dataset.
* Determine the best approach for analysis.

```{r ex7, echo=FALSE}
quiz(
question("Which of the following is NOT a responsibility of a data scientist in a one-on-one meeting?",
  answer("Being punctual and respectful."),
  answer("Explaining the analysis clearly."),
  answer("Changing the analysis to please a co-worker.", correct = TRUE),
  answer("Acknowledging limitations of the analysis.")
),
question("What is the purpose of discussing prior knowledge in a one-on-one meeting?",
  answer("To demonstrate expertise and knowledge."),
  answer("To understand the person's level of understanding.", correct = TRUE),
  answer("To avoid answering questions."),
  answer("To limit the scope of the analysis.")
)
)
```









