---
title: "Chapter 6: Remote work and task management"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
tutorial_options(exercise.checker = NULL)
```


## Chapter 6: Remote work and task management

In this tutorial, we will explore best practices and ideas for how to work remotely in a way that promotes not only your productivity but also your well being.

### 6.0.1 Goals for working remotely

```{r quiz0, echo=FALSE}
quiz(
  question("Which one of these is not a goal for working remotely?",
    answer("Creating a comfortable and conducive work area"),
    answer("Being healthy"),
    answer("Being unproductive", correct = TRUE),
    answer("Being productive")
  )
)
```


## 6.1 How to be healthy

To promote the healthiest version of yourself, ask yourself what you need to spend more time doing and what things you need to do less of. Some aspects of being healthy include:

* Adequate sleep and sleep patterns
* Balance and energetic meal plans
* Spending time with loving and supportive individuals
* Working reasonable hours - setting up boundaries
* Spending some time doing things you enjoy that refill your energy

```{r quiz1, echo=FALSE}
quiz(
  question("Which one of these is not a part of being healthy?",
    answer("Adequate sleep and sleep patterns"),
    answer("Skipping meals", correct = TRUE),
    answer("Working reasonable hours"),
    answer("Spending time with loving and supportive individuals")
  )
)
```


### 6.1.1 Define success

To set yourself up for success in regards to your health, you will need to start by defining what looks and feels healthy for you. Identify what steps are needed to create a healthier version of yourself.

```{r quiz2, echo=FALSE}
quiz(
  question("Which one of these is a part of defining success?",
    answer("Ignoring your well-being"),
    answer("Following an unhealthy diet"),
    answer("Identifying what steps are needed to create a healthier version of yourself", correct = TRUE),
    answer("Neglecting sleep")
  )
)
```


### 6.1.2 Form healthy habits

To change habits, we need to make goals that are SMART:

* Specific
* Measurable
* Achievable
* Relevant
* Time-bound

```{r quiz3, echo=FALSE}
quiz(
  question("Which one of these is not a part of SMART goals?",
    answer("Specific"),
    answer("Immeasurable", correct = TRUE),
    answer("Achievable"),
    answer("Time-bound")
  )
)
```


### 6.1.3 Know yourself

Remote work can be super powerful for being healthy but what is healthy might vary for different individuals. Remote work is great in that it can lend you flexibility to find routines and patterns that work best for promoting the healthiest form of you.

```{r quiz4, echo=FALSE}
quiz(
  question("What is the benefit of remote work?",
    answer("It allows you to work without any breaks"),
    answer("It can lend you flexibility to find routines and patterns that work best for promoting the healthiest form of you", correct = TRUE),
    answer("It makes you work longer hours"),
    answer("It isolates you from others")
  )
)
```


### 6.1.4 Self-reevaluate

Examine your workday and identify variables within your control that may have contributed to a good or bad day. Learn from your experiences and try to replicate what went well or make changes to improve the next day.

```{r quiz5, echo=FALSE}
quiz(
  question("What should you do to self-reevaluate?",
    answer("Dwell on the past"),
    answer("Ignore your experiences"),
    answer("Examine your workday and identify variables within your control that may have contributed to a good or bad day", correct = TRUE),
    answer("Do not make any changes")
  )
)
```


### 6.1.5 Reach out for help

```{r quiz6, echo=FALSE}
quiz(
  question("What is one of the most meaningful things you can do to promote your own healthy living?",
    answer("Ignore your problems"),
    answer("Keep everything to yourself"),
    answer("Avoid talking to others"),
    answer("Asking for help", correct = TRUE)
  )
)
```

## 6.2 How to be productive

### 6.2.1 Write things down

```{r quiz7, echo=FALSE}
quiz(
  question("Why is it important to write things down?",
    answer("To remember important tasks and goals", correct = TRUE),
    answer("To create more work for yourself"),
    answer("To practice handwriting"),
    answer("To have something to do")
  )
)
```


### 6.2.2 Define success

```{r quiz8, echo=FALSE}
quiz(
  question("What is the first step in setting up your work life for success?",
    answer("Ignoring your goals"),
    answer("Defining what success looks like in your career", correct = TRUE),
    answer("Focusing only on the negative aspects of your work"),
    answer("Copying someone else's career path")
  )
)
```


### 6.2.3 Identifying tasks

```{r quiz9, echo=FALSE}
quiz(
  question("What should you do to identify tasks that will help you reach your career goals?",
    answer("Ignore your goals"),
    answer("Research and talk to mentors about what you need to do to reach your desired career", correct = TRUE),
    answer("Focus only on the most difficult tasks"),
    answer("Avoid planning and let things happen")
  )
)
```

### 6.2.4 Break down tasks into bite-size chunks

```{r quiz10, echo=FALSE}
quiz(
  question("Why is it important to break down tasks into smaller, more manageable pieces?",
    answer("To make the task more intimidating"),
    answer("To avoid getting any work done"),
    answer("To make it easier to procrastinate"),
    answer("To make the task less overwhelming and more achievable", correct = TRUE)
  )
)
```


### 6.2.5 Form productive habits

```{r quiz11, echo=FALSE}
quiz(
  question("What is an important aspect of being productive and successful?",
    answer("Avoiding routines and habits"),
    answer("Engaging in a lot of mundane and repetitive habits", correct = TRUE),
    answer("Procrastinating as much as possible"),
    answer("Focusing only on the exciting aspects of work")
  )
)
```


### 6.2.6 Time Budgeting

```{r quiz12, echo=FALSE}
quiz(
  question("What should you do to effectively budget your time?",
    answer("Ignore your calendar and tasks"),
    answer("Plan tasks for the week and for the day", correct = TRUE),
    answer("Overload your schedule with unrealistic goals"),
    answer("Avoid setting up a schedule")
  )
)
```

#### 6.2.6.2 Put in one-time items

```{r quiz13, echo=FALSE}
quiz(
  question("What should you do when you make an appointment?",
    answer("Ignore it"),
    answer("Put it in your calendar", correct = TRUE),
    answer("Write it on a piece of paper")
  )
)
```


#### 6.2.6.2 Put in one-time items

```{r quiz14, echo=FALSE}
quiz(
  question("What should you fill the remaining time in your calendar with?",
    answer("Random events"),
    answer("Data science work", correct = TRUE),
    answer("Hobbies")
  )
)
```


### 6.2.7 Set up your workplace

```{r quiz15, echo=FALSE}
quiz(
  question("Which of the following is NOT an ideal feature for a remote workplace?",
    answer("A good WiFi signal"),
    answer("A reliable power source"),
    answer("A distracting environment", correct = TRUE)
  )
)
```


### 6.2.8 Plan out your tasks

```{r quiz16, echo=FALSE}
quiz(
  question("What is the first thing you should do when you sit down to do your data science work?",
    answer("Start working immediately"),
    answer("Take a break"),
    answer("Determine what tasks you would like to accomplish", correct = TRUE)
  )
)
```


### 6.2.9 Do the task

```{r quiz17, echo=FALSE}
quiz(
  question("What is a good way to stay focused on your task?",
    answer("Multitask"),
    answer("Using a timer to track your time", correct = TRUE),
    answer("Taking long breaks")
  )
)
```


### 6.2.10 Stick to it (you can do it!)

```{r quiz18, echo=FALSE}
quiz(
  question("What should you focus on while working on creating habits?",
    answer("Failures"),
    answer("Improvement", correct = TRUE),
    answer("Other people's progress")
  )
)
```


### 6.2.11 Self-reevaluate

```{r quiz19, echo=FALSE}
quiz(
  question("What should you do at the end of each day or week?",
    answer("Ignore your progress"),
    answer("Reflect on your task list and what you got done", correct = TRUE),
    answer("Focus only on your failures")
  )
)
```


### 6.2.12 Reach out for help

```{r quiz20, echo=FALSE}
quiz(
  question("What should you do if you are stuck on a particular task?",
    answer("Give up"),
    answer("Ask for help", correct = TRUE),
    answer("Wait for the solution to come")
  )
)
```



## Congratulations!

Congratulations! You have completed the tutorial on remote work and task management. Remember to always prioritize your well-being and strive for a healthy work-life balance while working remotely.
