---
title: "Chapters 7 - 12"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
tutorial_options(exercise.checker = NULL)
```


## 7. Forming Questions

### Learning Objectives

Through the completion of this section our goal is that you will be able to:

1. Recognize the general steps involved in a data science project
2. Practice forming data science questions
3. Understand the general categories for types of data science questions
4. Look at data and ask questions based on its contents

## 8 The Data Science Process

### 8.0.1 The Parts of a Data Science Project

```{r ex1, echo=FALSE}
quiz(
  question("What is the first part of a data science project?",
    answer("Clean the data"),
    answer("Form a question", correct = TRUE),
    answer("Share results")
  )
)
```


### 8.0.2 A Data Science Project Example

```{r ex2, echo=FALSE}
quiz
)
```


#### 8.0.2.3 Data Analysis

```{r ex3, echo=FALSE}
quiz(
 
)
```


#### 8.0.2.6 Get stats

```{r ex4, echo=FALSE}
quiz
)
```


#### 8.0.2.7 Interpret and communicate results

```{r ex5, echo=FALSE}
quiz
)
```


### 8.0.3 What you can build using R

#### 8.0.3.1 Prediction Risk of Opioid Overdoses in Providence, RI

```{r ex6, echo=FALSE}
quiz
```


### 8.0.4 Other Cool Data Science Projects

#### 8.0.4.1 Predicting movie ratings with IMDb data and R, by Dimiter Toshkov

```{r ex7, echo=FALSE}
quiz(
  question("What did Dimiter Toshkov predict using IMDb data?",
    answer("Box office revenue"),
    answer("Movie ratings", correct = TRUE),
    answer("The number of awards a movie will win")
  )
)
```



## Chapter 9: Types of Data Science Questions

### 9.0.0 Introduction

```{r ex8, echo=FALSE}
quiz(
  question("Which type of data science question aims to find unknown relationships between different variables?",
    answer("Descriptive"),
    answer("Exploratory", correct = TRUE),
    answer("Inferential"),
    answer("Predictive"),
    allow_retry = TRUE
  ),
    question("What is the term for a seemingly related relationship between two variables that are not actually causally related?",
    answer("Casual correlation"),
    answer("Strong correlation"),
    answer("Spurious correlation", correct = TRUE),
    answer("Direct correlation")
  ),
  question("What is the term for a seemingly related relationship between two variables that are not actually causally related?",
    answer("Casual correlation"),
    answer("Strong correlation"),
    answer("Spurious correlation", correct = TRUE),
    answer("Direct correlation")
  )
)
```


### 9.0.1 Examples of data science questions

```{r ex9, echo=FALSE}
quiz(
  question("What type of analysis is used for credit card fraud detection?",
    answer("Descriptive analysis"),
    answer("Exploratory analysis"),
    answer("Inferential analysis"),
    answer("Predictive analysis", correct = TRUE),
    allow_retry = TRUE
  )
)
```


```{r ex10, echo=FALSE}
quiz(
  question("What type of analysis is used for analyzing YouTube comments?",
    answer("Descriptive analysis", correct = TRUE),
    answer("Exploratory analysis"),
    answer("Inferential analysis"),
    answer("Predictive analysis")
  )
)
```


```{r ex11, echo=FALSE}
quiz(
  question("What type of analysis is used for analyzing the relationship between watching Sesame Street and children's test scores?",
    answer("Descriptive analysis"),
    answer("Exploratory analysis"),
    answer("Inferential analysis", correct = TRUE),
    answer("Predictive analysis")
  )
)
```

## Chapters 10: How to Learn

In this tutorial, we will discuss the importance of learning how to learn, embracing failure, having the right mindset, and asking for help.

### 10.0.1 Learning How To Learn

The best way to learn data science is by doing it. Throughout these lessons, practice the code you see and try it out on your own. If you get an error, that's okay! Google that error and try to learn from it!

### 10.0.1.1 The Mindset

Your mindset is very important to learning how to learn. Your goal should be to answer an interesting question. Your objective is not to memorize a bunch of functions but to use those functions to do something interesting. The path to accomplishing that goal may be circuitous, and you may experience setbacks before moving forward. That's okay!


### 10.0.1.2 The Path

When carrying out data science projects, there is always more than one way to solve a problem. Your path may be different from someone else's path. There is more than one way to approach and answer a question! Your approaches may not be identical, and that is more than okay!


### 10.0.1.3 Asking For Help

Data science is best done as a part of a community! Asking questions and brainstorming with others is ideally how data science projects are completed. No one knows everything, and that is okay and expected. When you're stuck, reach out for help, post your question online, or ask someone directly.


```{r ex12, echo=FALSE}
quiz(
  question("What is an important aspect of learning how to learn?",
    answer("Memorizing functions", correct = FALSE),
    answer("Embracing failure and having the right mindset", correct = TRUE),
    answer("Never asking for help", correct = FALSE)
  ),
  question("Which statement is true?",
    answer("There is only one correct way to solve a data science problem", correct = FALSE),
    answer("There can be multiple ways to solve a data science problem", correct = TRUE)
  ),
  question("When should you ask for help?",
    answer("Immediately without trying to solve the problem yourself", correct = FALSE),
    answer("After spending some time trying to solve the problem and searching online for a solution", correct = TRUE),
    answer("Never", correct = FALSE)
  )
)
```

## Chapter 11 RStudio and Projects

In this interactive tutorial, we will go through Chapter 11 of the course, focusing on RStudio and Projects.

### Logging in to RStudio Cloud

```{r ex13, echo=FALSE}
quiz(
  
  )
  question("How do you create a new RStudio project?",
    answer("Click on the 'New Project' button", correct = TRUE),
    answer("Press Ctrl + N"),
    answer("Go to File > New Project"),
    answer("Right-click on the workspace and select 'New Project'")
  ),
  question("How do you open a new R script?",
    answer("Go to File > New File > R Script", correct = TRUE),
    answer("Press Ctrl + R"),
    answer("Click on the 'New R Script' button"),
    answer("Right-click on the workspace and select 'New R Script'")
  ),
  question("What is the purpose of the Console in RStudio?",
    answer("To type and execute commands", correct = TRUE),
    answer("To store your data"),
    answer("To write and edit code"),
    answer("To visualize your data")
  )
)
```


### Logging in to RStudio Cloud

```{r ex14, echo=FALSE}
quiz(
  question("What should you see in the Environment quadrant?",
    answer("An object called 'example'", correct = TRUE),
    answer("An object called 'matrix'"),
    answer("An error message"),
    answer("Nothing")
  ),
  question("Which tab in the Environment quadrant contains the commands that have been run in this session?",
    answer("Data"),
    answer("History", correct = TRUE),
    answer("Packages"),
    answer("Files")
  )
)
```


### Making a new folder

```{r ex15, echo=FALSE}
quiz(
  question("Where can you create a new folder in RStudio?",
    answer("In the Source panel"),
    answer("In the Console panel"),
    answer("In the Environment panel"),
    answer("In the Files pane", correct = TRUE)
  )
)
```


### Files/Help/Plots/Packages/Viewer

```{r ex16, echo=FALSE}
quiz(
  question("Where do generated plots appear in RStudio?",
    answer("In the Source panel"),
    answer("In the Console panel"),
    answer("In the Environment panel"),
    answer("In the Plots tab", correct = TRUE)
  ),
  question("Where can you find the documentation for R packages and functions?",
    answer("In the Source panel"),
    answer("In the Console panel"),
    answer("In the Help tab", correct = TRUE),
    answer("In the Viewer tab")
  )
)
```


### Swirl


```{r ex17, echo=FALSE}
quiz(
  question("What does the swirl() function do?",
    answer("It starts a swirl module", correct = TRUE),
    answer("It installs the swirl package"),
    answer("It creates a new project in RStudio"),
    answer("It generates a plot")
  ),
  question("What is the keyboard shortcut to run a line of code in RStudio?",
    answer("Alt + Enter"),
    answer("Ctrl + Shift + Enter"),
    answer("Ctrl + Enter", correct = TRUE),
    answer("Shift + Enter")
  )
)
```

## Chapter 12: Your First Data Science Project

```{r ex18, echo=FALSE}
quiz(
  question("What is the first step in any data science project?",
    answer("Collecting and cleaning data"),
    answer("Creating models"),
    answer("Asking a question that can be answered with data", correct = TRUE),
    answer("Sharing the answer with other people")
  ),
  question("Which RStudio feature allows you to run a specific line or block of code?",
    answer("Shift + Enter"),
    answer("Ctrl + Enter", correct = TRUE),
    answer("Alt + Enter"),
    answer("Cmd + Enter")
  ),
  question("What is the correct file extension for an R Markdown file?",
    answer(".R"),
    answer(".Rmd", correct = TRUE),
    answer(".html"),
    answer(".md")
  ),
  question("Which file should you upload to your assignment folder?",
    answer("first_project.R"),
    answer("first_project.html"),
    answer("Both first_project.R and first_project.html"),
    answer("first_project.Rmd and first_project.nb.html", correct = TRUE)
  ),
 
)
```


