---
title: "Chapter 1: Intro: Welcome to DataTrail"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
tutorial_options(exercise.checker = NULL)
```


## Welcome to DataTrail

In this interactive tutorial, we will ask questions regarding chapter 1 of DataTrail, a 14-week educational initiative for young adults, high school, and GED graduates. DataTrail aims to equip members of underserved communities with the necessary skills and support required to work in the booming field of data science.

### Learning Objectives

1. Understand the purpose and objectives of DataTrail.
2. Learn about the mutually-intensive learning experience (MILE) approach.
3. Understand the whole-person ecosystem of support provided by DataTrail.


```{r quiz, echo=FALSE}
quiz(
  question("What does DataTrail aim to achieve?",
    answer("Equip members of underserved communities with data science skills", correct = TRUE),
    answer("Focus on training only technical skills"),
    answer("Offer a free 2-year program"),
    answer("Focus on only one specific data science tool")
  ),
  question("What is the MILE approach?",
    answer("A data science training methodology"),
    answer("A mutually-intensive learning experience", correct = TRUE),
    answer("A programming language"),
    answer("A new data science tool")
  ),
  question("What is the main target group for DataTrail?",
    answer("BIPOC individuals and their potential employers", correct = TRUE),
    answer("College graduates"),
    answer("Data science professionals"),
    answer("Children and teenagers")
  ),
  question("Which institution offers DataTrail?",
    answer("Johns Hopkins Bloomberg School of Public Health", correct = TRUE),
    answer("Harvard University"),
    answer("Stanford University"),
    answer("Massachusetts Institute of Technology")
  ),
  question("What are the two main components of the DataTrail program?",
    answer("MILE and whole-person ecosystem of support", correct = TRUE),
    answer("Online courses and in-person workshops"),
    answer("Theoretical courses and practical projects"),
    answer("Certification exams and job placement services")
  ),
  question("What is the role of mentors in the DataTrail MILE?",
    answer("To engage in anti-racism and mentorship training", correct = TRUE),
    answer("To teach scholars technical skills"),
    answer("To provide job opportunities directly"),
    answer("To offer financial support to scholars")
  )
)
```

## Congratulations!

You have now completed the introductory chapter of DataTrail. In the next chapter, you'll learn about finding help and resources for your data science journey.

