---
title: "Chapter 4: Working Offline vs Online"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
tutorial_options(exercise.checker = NULL)
```


## 4.0 Cloud computing

```{r quiz0, echo=FALSE}
quiz(
  question("What does cloud computing involve?",
    answer("Applications and software running on personal computers"),
    answer("Applications and software running on shared data centers", correct = TRUE),
    answer("Storing data on external hard drives")
  ),
  question("What is the main advantage of cloud computing for data analysis?",
    answer("Less need for personal computer maintenance"),
    answer("Increased security and privacy"),
    answer("Increased computing power and reduced cost for high-capacity computers", correct = TRUE)
  )
)
```


### 4.0.2 What are the advantages of using the cloud?

```{r quiz1, echo=FALSE}
quiz(
  question("What is a major advantage of cloud storage?",
    answer("Files are safe even if the computer is lost or damaged", correct = TRUE),
    answer("Increased computing power"),
    answer("No need for an Internet connection")
  ),
  question("How does working with the cloud affect software maintenance?",
    answer("Increases the user's responsibility to maintain software"),
    answer("The responsibility of maintaining software is on the service provider", correct = TRUE),
    answer("There is no difference in software maintenance")
  )
)
```


### 4.0.3 What are the disadvantages of using the cloud?

```{r quiz2, echo=FALSE}
quiz(
  question("What is a major disadvantage of working on the cloud?",
    answer("Increased computing power"),
    answer("Need for an Internet connection to access storage and computing power", correct = TRUE),
    answer("Decreased security and privacy")
  ),
  question("What is a good practice to secure your cloud-based accounts?",
    answer("Use a weak password for easy memorization"),
    answer("Choose two-factor authentication whenever it is offered", correct = TRUE),
    answer("Connect to any available network")
  )
)
```


### 4.0.4 Google Drive

```{r quiz3, echo=FALSE}
quiz(
  question("What is the advantage of storing files on Google Drive?",
    answer("Files are accessible only from your personal computer"),
    answer("Files are stored online and can be accessed from any Internet connected computer", correct = TRUE),
    answer("Files will be lost if you lose your Chromebook")
  ),
  question("How do you make Google Drive files available offline on a Chromebook?",
    answer("It is not possible to make Google Drive files available offline"),
    answer("Open the Google Drive app and enable the 'Offline' setting in Settings", correct = TRUE),
    answer("Move all files from Google Drive to the 'Downloads' folder")
  )
)
```


### 4.0.5 Example: editing a text file offline

```{r quiz4, echo=FALSE}
quiz(
  question("What app is commonly used for offline text editing?",
    answer("Google Sheets"),
    answer("Google Slides"),
    answer("Google Docs", correct = TRUE)
  ),
  question("How do you create a new document in Google Docs?",
    answer("Click on the Google Docs icon and click on the plus sign", correct = TRUE),
    answer("Open the Google Drive app and enable the 'Offline' setting"),
    answer("Move files from Google Drive to the 'Downloads' folder")
  )
)
```


### 4.0.6 Offline Apps

```{r quiz5, echo=FALSE}
quiz(
  question("Which of the following apps have offline functionality?",
    answer("Google Docs", correct = TRUE),
    answer("Google Sheets", correct = TRUE),
    answer("Google Slides", correct = TRUE),
    answer("Facebook", correct = FALSE)
  ),
  question("What should you do to find apps with offline functionality on the Google Web Store?",
    answer("Search for apps that mention offline functionality", correct = TRUE),
    answer("Check the number of downloads", correct = FALSE),
    answer("Sort apps by rating", correct = FALSE),
    answer("Look for apps with a cloud icon", correct = FALSE)
  )
)
```


## 4.1 Where Are Files Stored?

```{r quiz6, echo=FALSE}
quiz(
  question("Where are most files stored on a Chromebook?",
    answer("Local storage", correct = FALSE),
    answer("Google Drive or Dropbox", correct = TRUE),
    answer("CDs or DVDs", correct = FALSE),
    answer("External hard drives", correct = FALSE)
  ),
  question("How can you check the remaining storage space on your Chromebook?",
    answer("Check the device's settings", correct = FALSE),
    answer("Click the three dots on the upper right-hand side of the Files app", correct = TRUE),
    answer("Search for 'storage' on Google", correct = FALSE),
    answer("Ask the Chromebook", correct = FALSE)
  )
)
```


### 4.1.1 Where is the local storage?

```{r quiz7, echo=FALSE}
quiz(
  question("How do you access the Files App on a Chromebook?",
    answer("Click on the Launcher circle and then click on the Files App icon", correct = TRUE),
    answer("Type 'Files App' into the Google search bar", correct = FALSE),
    answer("Right-click on the desktop and select 'Files'", correct = FALSE),
    answer("Press the 'F' key on the keyboard", correct = FALSE)
  ),
  question("What is the purpose of the Downloads folder on a Chromebook?",
    answer("To store downloaded movies and music", correct = FALSE),
    answer("To store temporary internet files", correct = FALSE),
    answer("To store all files that are saved directly on the Chromebook", correct = TRUE),
    answer("To store files that are shared with other users", correct = FALSE)
  )
)
```




## Congratulations!

You have completed all the quiz questions for chapter 4 and now (hopefully) have a better handle on offline and online ways of working and storing files!
