---
title: "7. Forming Questions and 8. The Data Science Process"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
tutorial_options(exercise.checker = NULL)
```


## 7. Forming Questions

### Learning Objectives

Through the completion of this section our goal is that you will be able to:

1. Recognize the general steps involved in a data science project
2. Practice forming data science questions
3. Understand the general categories for types of data science questions
4. Look at data and ask questions based on its contents

## 8 The Data Science Process

### 8.0.1 The Parts of a Data Science Project

```{r quiz0, echo=FALSE}
quiz(
  question("What is the first part of a data science project?",
    answer("Clean the data"),
    answer("Form a question", correct = TRUE),
    answer("Share results")
  )
)
```


### 8.0.2 A Data Science Project Example

```{r quiz1, echo=FALSE}
quiz(
  question("What is Hilary Parker's question?",
    answer("Is Hilary/Hillary really the most rapidly poisoned name in recorded American history?", correct = TRUE),
    answer("What is the most popular baby name in recorded American history?"),
    answer("How do baby name trends change over time?")
  )
)
```


#### 8.0.2.3 Data Analysis

```{r quiz2, echo=FALSE}
quiz(
  question("What is one purpose of exploring and plotting the data?",
    answer("To understand the data better", correct = TRUE),
    answer("To make the data look pretty"),
    answer("To convince people that your analysis is correct")
  )
)
```


#### 8.0.2.6 Get stats

```{r quiz3, echo=FALSE}
quiz(
  question("In Hilary's analysis, what did she find in her preliminary results?",
    answer("Hilary was the most poisoned name"),
    answer("Hilary was the least poisoned name"),
    answer("Hilary was sixth on the list of poisoned names", correct = TRUE)
  )
)
```


#### 8.0.2.7 Interpret and communicate results

```{r quiz4, echo=FALSE}
quiz(
  question("What is an important part of any data science project?",
    answer("Effectively communicating the results", correct = TRUE),
    answer("Using fancy visualization techniques"),
    answer("Having a large dataset")
  )
)
```


### 8.0.3 What you can build using R

#### 8.0.3.1 Prediction Risk of Opioid Overdoses in Providence, RI

```{r quiz5, echo=FALSE}
quiz(
  question("What did the students at the University of Pennsylvania predict?",
    answer("Risk of opioid overdoses in Providence, Rhode Island", correct = TRUE),
    answer("Risk of traffic accidents in Providence, Rhode Island"),
    answer("Risk of heart disease in Providence, Rhode Island")
  )
)
```


### 8.0.4 Other Cool Data Science Projects

#### 8.0.4.1 Predicting movie ratings with IMDb data and R, by Dimiter Toshkov

```{r quiz6, echo=FALSE}
quiz(
  question("What did Dimiter Toshkov predict using IMDb data?",
    answer("Box office revenue"),
    answer("Movie ratings", correct = TRUE),
    answer("The number of awards a movie will win")
  )
)
```


## Congratulations!

Congratulations! You have completed the tutorial on understanding the data science process and are ready to start formulating more specific data science questions.
