---
title: "Chapters 44 - 48"
output:
  learnr::tutorial:
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
library(ggplot2)
library(dplyr)
library(knitr)
library(kableExtra)
library(plotly)


knitr::opts_chunk$set(echo = TRUE)

gradethis::gradethis_setup()
```


## Chapter 44: Data Tables

### What are Data Tables?

Data tables are a way to display data in a structured, tabular format. Data tables can be exploratory, helping you understand the data, or explanatory, displaying information in a table format to others.

### When to Make a Table

Tables are effective when you want to display summary information about a dataset or when you want to display top results from an analysis.

```{r}
# Let's use the `mpg` dataset from the `ggplot2` package for our examples
data(mpg)
head(mpg)
```

### What to Consider When Making A Table

When making a table, it's important to consider the ordering, spacing, labels, significant digits, title or caption, and the source of the data.

### Exercise 1: Making a Summary Table

Let's create a summary table that displays the average cty and hwy mileage for each class of vehicle in the mpg dataset.

```{r ex1, exercise=TRUE}
# Write your code here
```

```{r ex1-setup}
```

```{r ex1-solution}
mpg %>%
  group_by(class) %>%
  summarise(cty = mean(cty), hwy = mean(hwy)) %>%
  kable()
```

```{r ex1-check}
grade_code()
```


### Exercise 2: Displaying Top Results

Let's create a table that displays the top 5 classes of vehicles with the highest average `hwy` mileage.

```{r ex2, exercise=TRUE}
# Write your code here
```

```{r ex2-setup}
```

```{r ex2-solution}
mpg %>%
  group_by(class) %>%
  summarise(hwy = mean(hwy)) %>%
  top_n(5, hwy) %>%
  kable()
```

```{r ex2-check}
grade_code()
```

### Conclusion

Remember, when creating a table, keep in mind the ordering and spacing, labels, number of significant digits, title or caption, and the source of your data. Always ensure your tables are concise, clear, and easy to understand. In the next tutorial, we will go into more depth about data tables and explore some additional features and considerations. Happy coding!

## Chapter 45: Tables in R

### Introduction

In this tutorial, we will learn how to create informative tables in R using the `mpg` dataset from the `ggplot2` package. This dataset contains fuel economy data from 1999 to 2008 for 38 popular models of cars.

#### Getting started with the data

Let's start by examining the `mpg` dataset. Our main interest is to summarize the data based on the classes of vehicles.

```{r}
library(ggplot2)
head(mpg)
```

#### Exercise 1: Summarizing the Data

Let's create a summary table for each class of vehicles. We want to calculate the number of vehicles (count), minimum highway mileage (min_hwy), average highway mileage (avg_hwy), and maximum highway mileage (max_hwy) for each class. Save the table to a variable called mpg_summary.

```{r ex3, exercise=TRUE}
library(dplyr)
# Write your code here
```

```{r ex3-setup}
```

```{r ex3-solution}
mpg_summary <- mpg %>%
  group_by(class) %>%
  summarise(
    count = n(),
    min_hwy = min(hwy),
    avg_hwy = mean(hwy),
    max_hwy = max(hwy)
  )
```

```{r ex3-check}
grade_code()
```

#### Enhancing the Table Display

The default R output is functional but lacks aesthetic appeal. We can enhance the table output using the `kable()` function from the `knitr` package.

```{r, echo=FALSE}
mpg_summary <- mpg %>%
  group_by(class) %>%
  summarise(
    count = n(),
    min_hwy = min(hwy),
    avg_hwy = mean(hwy),
    max_hwy = max(hwy)
  )
```

```{r}
knitr::kable(mpg_summary)
```

#### Exercise 2: Improving the Table

Now, let's further improve the table by addressing the following issues:

1. Rename column names to be more informative.
2. Restrict the average highway mileage (avg_hwy) to 2 significant digits.
3. Add a caption to the table.
4. Shade alternate rows for better readability.


```{r ex4, exercise=TRUE}
library(knitr)
library(kableExtra)
# Write your code here

```

```{r ex4-setup}
mpg_summary <- mpg %>%
  group_by(class) %>%
  summarise(
    count = n(),
    min_hwy = min(hwy),
    avg_hwy = mean(hwy),
    max_hwy = max(hwy)
  )
```

```{r ex4-solution}
mpg_summary %>%
  rename(
    "Vehicle Class" = class,
    "Number of Vehicles" = count,
    "Minimum Highway Mileage" = min_hwy,
    "Average Highway Mileage" = avg_hwy,
    "Maximum Highway Mileage" = max_hwy
  ) %>%
  kable(digits = 2, 
        caption = "Table 1: Summary of Highway Mileage by Vehicle Class", 
        "html") %>%
  kable_styling("striped")

```

```{r ex4-check}
grade_code()
```

### Conclusion

This tutorial introduced the basics of creating informative tables in R. Remember, the best way to learn is by practicing. So, feel free to play around with different functions and options to make your tables even better. Happy coding!

## Chapter 46: Multiple Plots in R

### Introduction

The `patchwork` package in R allows you to easily combine multiple plots generated with `ggplot2`. This tutorial will guide you through the process of creating, combining, and customizing multiple plots. We'll use the `mpg` dataset from the `ggplot2` package for this tutorial.

First, let's load the required libraries and data.

```{r}
library(ggplot2)
library(patchwork)
data(mpg)
```


### Creating Basic Plots

We'll begin by creating two plots: a scatter plot of `displ` vs. `hwy`, and a boxplot of `class` vs. `hwy`.

```{r}
p1 <- ggplot(mpg) + geom_point(aes(displ, hwy))
p2 <- ggplot(mpg) + geom_boxplot(aes(class, hwy, group = class))

p1
p2
```

Now, let's combine these plots side by side using `patchwork`.

```{r}
p1 + p2
```

### Customizing Layout

You can also arrange the plots vertically using plot_layout() and specifying the number of columns as 1.

``` {r}
p1 + p2 + plot_layout(ncol = 1)
```

### Interactive Coding Exercise 1

Let's now try to create another plot `p3` that is a bar plot of `class` and arrange it below `p1` and `p2`. Set the heights such that `p1` and `p2` are twice as large as `p3`.

```{r ex5, exercise=TRUE}
# Create the bar plot p3

# Arrange the plots
```

```{r ex5-setup}
p1 <- ggplot(mpg) + geom_point(aes(displ, hwy))
p2 <- ggplot(mpg) + geom_boxplot(aes(class, hwy, group = class))
```

```{r ex5-solution}
# Create the bar plot p3
p3 <- ggplot(mpg) + geom_bar(aes(class))

# Arrange the plots
p1 + p2 + p3 + plot_layout(ncol = 1, heights = c(2, 2, 1))
```

```{r ex5-check}
grade_code()
```

### Additional Operators

You can also combine plots in more complex ways using additional operators. The pipe (`|`) and slash (`/`) operators arrange plots horizontally and vertically, respectively.

```{r, echo=FALSE}
p3 <- ggplot(mpg) + geom_bar(aes(class))
```

```{r}
(p1 | p2) / p3
```

#### Interactive Coding Exercise 2

Let's create a fourth plot `p4` that is a histogram of `hwy`. Then, arrange `p1` and `p2` horizontally on top of `p3` and `p4` arranged vertically. Also, apply the `theme_bw()` to all plots.

```{r ex6, exercise=TRUE}
# Create the histogram p4
p4 <- ggplot(mpg) + geom_histogram(aes(hwy))

# Arrange the plots and apply the theme
((p1 | p2) / (p3 | p4)) & theme_bw()

```

```{r ex6-setup}
p1 <- ggplot(mpg) + geom_point(aes(displ, hwy))
p2 <- ggplot(mpg) + geom_boxplot(aes(class, hwy, group = class))
p3 <- ggplot(mpg) + geom_bar(aes(class))
```

```{r ex6-solution}
# Create the histogram p4
p4 <- ggplot(mpg) + geom_histogram(aes(hwy))

# Arrange the plots and apply the theme
((p1 | p2) / (p3 | p4)) & theme_bw()

```

```{r ex6-check}
grade_code()
```


### Conclusion

In this tutorial, we learned how to use the `patchwork` package to create and combine multiple `ggplot2` plots. We also learned how to customize the layout of combined plots and apply themes to them. Keep practicing and experimenting with different combinations of plots to get more comfortable with `patchwork`!

## Chapter 47: Advanced Data Visualization

In this tutorial, we will explore some advanced data visualization techniques that can be implemented in R. Specifically, we will focus on creating interactive and animated graphics using the `plotly` package. Let's dive in!

### Interactive Graphics

So far, you've been creating static graphics in R. While they are excellent for conveying information, they lack the ability to react to user input. Interactive graphics, on the other hand, allow users to engage with the displayed data. For instance, an interactive graphic might let you hover over data points to display additional information or zoom into a specific part of the graph.

### Animated Graphics

Animated graphics are another form of non-static visualization. Instead of responding to user input like interactive graphics, animated graphics display a sequence of static plots in a specific order, similar to a video. This type of graphic is useful when you want to illustrate changes over time.

### Interactive Graphics with plotly

The `plotly` package provides tools for translating `ggplot2` graphs into interactive web-based versions. Let's see how we can use `plotly` to make our plots interactive.

```{r}
# Load the necessary packages
library(ggplot2)
library(plotly)
```


```{r ex7, exercise=TRUE}
# Create a ggplot2 object
p <- ggplot(mtcars, aes(x = factor(cyl), y = mpg)) +
  geom_boxplot() +
  geom_point()

# Convert the ggplot2 object to an interactive plot
```

```{r ex7-setup}
# Create a ggplot2 object
p <- ggplot(mtcars, aes(x = factor(cyl), y = mpg)) +
  geom_boxplot() +
  geom_point()
```

```{r ex7-solution}
# Convert the ggplot2 object to an interactive plot
p <- ggplotly(p)
p
```

```{r ex7-check}
grade_code()
```

### plotly in RMarkdown reports

Plotly objects can be incorporated directly into RMarkdown reports as long as the .Rmd file is knitted into an HTML document. However, if a plotly object is knitted in a non-HTML format, it will be displayed as a .png screenshot of the graph.

### Summary

In this tutorial, we've discussed how to generate interactive and animated graphics in R using the `plotly` package. We hope you now have a better understanding of how to use these advanced data visualization techniques in your own work. Feel free to explore more about `plotly` and other visualization packages in R!

```{r ex8, echo=FALSE}
quiz(
  question("What is an interactive graphic?",
    answer("A graphic that changes over time."),
    answer("A graphic that reacts to user input.", correct = TRUE),
    answer("A graphic that can be embedded into an RMarkdown report."),
    answer("A graphic that can be saved as a .png screenshot.")
  ),
  question("What is an animated graphic?",
    answer("A graphic that reacts to user input."),
    answer("A graphic that changes over time.", correct = TRUE),
    answer("A graphic that can be embedded into an RMarkdown report."),
    answer("A graphic that can be saved as a .png screenshot.")
  )
)
```







