---
title: "Chapter 2: Finding Help"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
tutorial_options(exercise.checker = NULL)
```


## Finding Help

In this tutorial, you will learn how to find help and resources related to data science and the R programming language.

### Learning Objectives

1. Understand the importance of seeking help and using resources.
2. Learn how to search the internet effectively for answers.
3. Become familiar with specific websites and resources for finding help in R.
4. Learn about AI ChatBots as a resource for help.


```{r quiz0, echo=FALSE}
quiz(
  question("Why is it important to seek help and use resources?",
    answer("To save time and find solutions to problems", correct = TRUE),
    answer("To avoid learning anything"),
    answer("To rely only on others for answers"),
    answer("To avoid using search engines")
  ),
  question("What are some guidelines for effective Google searches?",
    answer("Use full sentences and correct grammar"),
    answer("Use the fewest words possible and be specific", correct = TRUE),
    answer("Ask only general questions"),
    answer("Avoid using specific websites for help")
  )
)
```

## Practice: Searching for Help

Let's practice searching for help on a specific topic related to R programming. Type the following search query into Google:

```
R create dataframe from vectors
```

```{r quiz1, echo=FALSE}
quiz(
  question("Which website from the search results is a common source of help for R programming?",
    answer("Stack Overflow", correct = TRUE),
    answer("Wikipedia"),
    answer("Facebook"),
    answer("Yahoo Answers")
  )
)
```

### Chapter 2: Additional Questions

```{r quiz2, echo=FALSE}
quiz(
  question("Which programming language will be the main focus of the coursework?",
    answer("R", correct = TRUE),
    answer("Python"),
    answer("Java"),
    answer("C++")
  ),
  question("Which search engine is the most common for finding help?",
    answer("Google", correct = TRUE),
    answer("Bing"),
    answer("Yahoo"),
    answer("DuckDuckGo")
  ),
  question("What is one of the specific websites where you can find help related to programming in general?",
    answer("Stack Overflow", correct = TRUE),
    answer("Instagram"),
    answer("Pinterest"),
    answer("LinkedIn")
  ),
  question("What is an example of how you can use AI ChatBots like ChatGPT?",
    answer("Asking ChatGPT to explain a piece of code", correct = TRUE),
    answer("Asking ChatGPT to write your whole project"),
    answer("Asking ChatGPT for personal advice"),
    answer("Asking ChatGPT to debug your code automatically")
  )
)
```

## Congratulations!

You have now completed the "Finding Help" chapter of DataTrail. You have learned the importance of seeking help, how to search effectively, and become familiar with various resources to assist you in your data science journey. Keep practicing and don't hesitate to seek help when needed!
