---
title: "Chapter 3: Understanding Your Chromebook"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
tutorial_options(exercise.checker = NULL)
```


## 3.1 What is a Chromebook?

```{r quiz0, echo=FALSE}
quiz(
  question("What is the main purpose of a Chromebook?",
    answer("To play video games"),
    answer("To use as a dedicated offline workstation"),
    answer("To work primarily on the web", correct = TRUE),
    answer("To run heavy computational tasks")
  ),
  question("What is 'cloud computing'?",
    answer("Storing physical computers in the sky"),
    answer("Using the Internet to access tools and computers to do your work", correct = TRUE),
    answer("A method of cooling down computers"),
    answer("A type of computer virus")
  )
)
```

## 3.2 Chrome OS

```{r quiz1, echo=FALSE}
quiz(
  question("What are the three different ways to add new software to a Chromebook?",
    answer("Chrome Apps, Chrome Extensions, Android Apps", correct = TRUE),
    answer("Windows Apps, Linux Apps, Mac Apps"),
    answer("Chrome Apps, Firefox Extensions, Safari Extensions"),
    answer("Google Drive, Dropbox, OneDrive")
  ),
  question("What are Google Docs, Slides, and Sheets?",
    answer("Online file storage services"),
    answer("Video conferencing tools"),
    answer("Chrome Apps for creating and editing documents, presentations, and spreadsheets", correct = TRUE),
    answer("Social media platforms")
  )
)
```

### 3.2.1 Chrome "Apps"

```{r quiz2, echo=FALSE}
quiz(
  question("What is the main difference between a Chrome App and a Chrome Extension?",
    answer("Chrome Apps run inside the browser, while Chrome Extensions modify the browser itself", correct = TRUE),
    answer("Chrome Apps modify the browser itself, while Chrome Extensions run inside the browser"),
    answer("Chrome Apps are for entertainment, while Chrome Extensions are for productivity"),
    answer("Chrome Apps are for productivity, while Chrome Extensions are for entertainment")
  ),
  question("What do Google Docs, Slides, and Sheets have in common?",
    answer("They are all social media platforms"),
    answer("They are all Chrome Extensions"),
    answer("They are all file storage services"),
    answer("They are all Chrome Apps for creating and editing different types of documents", correct = TRUE)
  )
)
```

### 3.2.2 Where do Chromebook Apps live?

```{r quiz3, echo=FALSE}
quiz(
  question("What is the purpose of the 'Shelf' on a Chromebook?",
    answer("To store your physical books and documents"),
    answer("To provide easy access to your most frequently used Chrome Apps", correct = TRUE),
    answer("To store your passwords and login information"),
    answer("To keep track of your browsing history")
  ),
  question("Question 2: How do you open the screen with all your installed apps on a Chromebook?",
    answer("Press the power button"),
    answer("Click the Launcher button on the lower left-hand side of the screen", correct = TRUE),
    answer("Press the escape key"),
    answer("Swipe up")
  )
)
```


### 3.2.5 The Chrome Web Store and Chrome Apps

```{r quiz4, echo=FALSE}
quiz(
  question("How can you access the Chrome Web Store on a Chromebook?",
    answer("Click on the launcher button, then find and click the Web Store icon"),
    answer("Type 'chrome web store' in the search bar", correct = TRUE),
    answer("Press the Web Store key on the keyboard")
  ),
  question("Which of the following is true about Chrome Apps?",
    answer("They only work when your Chromebook is offline"),
    answer("They are only available on Android devices"),
    answer("They can be run from the web browser and sometimes require installation", correct = TRUE)
  ),
  question("What is the main purpose of the StackEdit app?",
    answer("To manage your passwords"),
    answer("To write and save Markdown files", correct = TRUE),
    answer("To display funny pictures when you open a new tab")
  )
)
```


### 3.2.6 Chrome Extensions

```{r quiz5, echo=FALSE}
quiz(
  question("What are Chrome Extensions?",
    answer("Software programs that modify the way that the Chrome browser works", correct = TRUE),
    answer("Websites that you can save for offline reading"),
    answer("Applications that run on Android devices")
  ),
  question("How can you install Chrome Extensions?",
    answer("By going to the Chrome Web Store and searching for the desired extension", correct = TRUE),
    answer("By visiting the extension's website and clicking 'Install'"),
    answer("By downloading the extension from an external website and manually installing it")
  ),
  question("What does the Pocket Chrome extension do?",
    answer("Allows you to save webpages for offline reading", correct = TRUE),
    answer("Displays a funny picture every time you open a new tab"),
    answer("Helps you manage your passwords")
  )
)
```


## 3.5 Chromebook Shortcuts

```{r quiz6, echo=FALSE}
quiz(
  question("What does the keyboard shortcut 'ctrl+n' do on a Chromebook?", 
                  answer("Open a new Chrome window", correct = TRUE),
                  answer("Close an open Chrome window or tab"),
                  answer("Bookmark a page")),
  
  question("What is the function of the refresh key?", 
                  answer("Takes you back to the previous webpage"),
                  answer("Takes you forward to the next webpage"),
                  answer("Refreshes the current webpage", correct = TRUE)),
  
  question("Which key combination takes a screenshot of the entire screen on a Chromebook?", 
                  answer("ctrl+showwindows", correct = TRUE),
                  answer("ctrl+shift+showwindows"),
                  answer("ctrl+lock")),
  question("Which key combination allows you to zoom in on a Chromebook?", 
                  answer("ctrl+plus/equals", correct = TRUE),
                  answer("ctrl+minus/underscore"),
                  answer("ctrl+f")),
  
  question("How do you search for a specific word or phrase on a webpage using a keyboard shortcut?", 
                  answer("ctrl+z"),
                  answer("ctrl+f", correct = TRUE),
                  answer("ctrl+c")),
  
  question("Which key combination allows you to copy selected text on a Chromebook?", 
                  answer("ctrl+v"),
                  answer("ctrl+x"),
                  answer("ctrl+c", correct = TRUE))
)
```


## 3.6 Chromebook Security Quiz


```{r quiz7, echo=FALSE}
quiz(
  question("What is one of the characteristics of a good password?", 
                  answer("Short and simple"),
                  answer("Easy for other people to guess"),
                  answer("Long and easy for you to remember, but hard for others to guess", correct = TRUE)),
  
  question("Which setting should you enable to require a password when waking your Chromebook from sleep?", 
                  answer("Show screen lock when waking from sleep", correct = TRUE),
                  answer("Manage Other People"),
                  answer("Two step verification")),
  
  question("What is the purpose of two-step verification?", 
                  answer("To make it easier to log in to your account"),
                  answer("To require both a password and a code sent to your phone to access your account", correct = TRUE),
                  answer("To manage who can access your Chromebook"))
)
```

### 3.6.5 Managing apps and devices

```{r quiz8, echo=FALSE}
quiz(
  question("Where can you monitor and manage apps and devices that have access to your Google account information?", 
                  answer("https://myaccount.google.com/security", correct = TRUE),
                  answer("https://myaccount.google.com/apps"),
                  answer("https://myaccount.google.com/devices")),
  
  question("How often should you check your account security page for any unrecognized events or activity?", 
                  answer("Every week"),
                  answer("Every month or so", correct = TRUE),
                  answer("Every year"))
)
```

## 3.7 Updating your Chromebook

```{r quiz9, echo=FALSE}
quiz(
  question("What does updating your Chromebook's operating system (OS) do?", 
                  answer("Slows down the system"),
                  answer("Fixes bugs, adds new features, and/or improves security", correct = TRUE),
                  answer("Changes the user interface drastically")),
  
  question("When does your Chromebook check for and apply available updates?", 
                  answer("Every time you power it on", correct = TRUE),
                  answer("Every week"),
                  answer("Only when you manually check for updates"))
)
```


## 3.8 Getting Help with a Chromebook

```{r quiz10, echo=FALSE}
quiz(
  question("Which of the following is NOT a common Chromebook issue category?", 
                  answer("Operating System Issues"),
                  answer("Internet Connection Problems"),
                  answer("Hardware Malfunction", correct = TRUE)),
  
  question("Where can you find Chromebook support and ask questions about your device?", 
                  answer("https://support.apple.com/chromebook"),
                  answer("https://support.google.com/chromebook", correct = TRUE),
                  answer("https://support.microsoft.com/chromebook"))
)
```


## Congratulations!

You have completed all the quiz questions for chapter 3 and now (hopefully) have a better handle on working with your chromebook!
