---
title: "Chapter 11 RStudio and Projects"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyr)
library(dplyr)
knitr::opts_chunk$set(echo = TRUE)
tutorial_options(exercise.checker = NULL)
```


## Chapter 11 RStudio and Projects

In this interactive tutorial, we will go through Chapter 11 of the course, focusing on RStudio and Projects.

### Logging in to RStudio Cloud

```{r quiz0, echo=FALSE}
quiz(
  question("What is RStudio Cloud?",
    answer("A cloud-based version of RStudio", correct = TRUE),
    answer("A cloud-based version of R"),
    answer("A data storage service"),
    answer("A data visualization tool"),
    allow_retry = TRUE
  ),
  question("How do you log in to RStudio Cloud for this course?",
    answer("Using your Google account", correct = TRUE),
    answer("Using your GitHub account"),
    answer("Using your Microsoft account"),
    answer("Creating a new RStudio Cloud account")
  ),
  question("How do you create a new RStudio project?",
    answer("Click on the 'New Project' button", correct = TRUE),
    answer("Press Ctrl + N"),
    answer("Go to File > New Project"),
    answer("Right-click on the workspace and select 'New Project'")
  ),
  question("How do you open a new R script?",
    answer("Go to File > New File > R Script", correct = TRUE),
    answer("Press Ctrl + R"),
    answer("Click on the 'New R Script' button"),
    answer("Right-click on the workspace and select 'New R Script'")
  ),
  question("What is the purpose of the Console in RStudio?",
    answer("To type and execute commands", correct = TRUE),
    answer("To store your data"),
    answer("To write and edit code"),
    answer("To visualize your data")
  )
)
```


### Logging in to RStudio Cloud

```{r quiz1, echo=FALSE}
quiz(
  question("What should you see in the Environment quadrant?",
    answer("An object called 'example'", correct = TRUE),
    answer("An object called 'matrix'"),
    answer("An error message"),
    answer("Nothing")
  ),
  question("Which tab in the Environment quadrant contains the commands that have been run in this session?",
    answer("Data"),
    answer("History", correct = TRUE),
    answer("Packages"),
    answer("Files")
  )
)
```


### Making a new folder

```{r quiz2, echo=FALSE}
quiz(
  question("Where can you create a new folder in RStudio?",
    answer("In the Source panel"),
    answer("In the Console panel"),
    answer("In the Environment panel"),
    answer("In the Files pane", correct = TRUE)
  )
)
```


### Files/Help/Plots/Packages/Viewer

```{r quiz3, echo=FALSE}
quiz(
  question("Where do generated plots appear in RStudio?",
    answer("In the Source panel"),
    answer("In the Console panel"),
    answer("In the Environment panel"),
    answer("In the Plots tab", correct = TRUE)
  ),
  question("Where can you find the documentation for R packages and functions?",
    answer("In the Source panel"),
    answer("In the Console panel"),
    answer("In the Help tab", correct = TRUE),
    answer("In the Viewer tab")
  )
)
```


### Swirl


```{r quiz4, echo=FALSE}
quiz(
  question("What does the swirl() function do?",
    answer("It starts a swirl module", correct = TRUE),
    answer("It installs the swirl package"),
    answer("It creates a new project in RStudio"),
    answer("It generates a plot")
  ),
  question("What is the keyboard shortcut to run a line of code in RStudio?",
    answer("Alt + Enter"),
    answer("Ctrl + Shift + Enter"),
    answer("Ctrl + Enter", correct = TRUE),
    answer("Shift + Enter")
  )
)
```



Now that you've completed the quiz, you should have a better understanding of RStudio, how to create projects and work with R scripts, and the purpose of the Console. Keep practicing and exploring RStudio to become more familiar with its features and functionalities. Happy coding!
